\appendix
{\LARGE \textbf{APPENDICES}}\\

We give here some details about the inference in our TCM implementation outlined in section \ref{sec:methodology_tcm}.

\section{Click probability}
For $P(F_{i,j}=1)$ we introduce a variable $f_{i,j}$, which will be derived later. \\
By assumption that $M_i, E_{i,j},R_{i,j}$and$F_{i,j}$ are independent, click probability can be formularize as:
\begin{align}
P(C_{i,j} = 1)
&= P(M_i=1) * P(E_{i,j}=1) * P(R_{i,j}=1) * P(F_{i,j} = 1) \\
&= \alpha_1 * \beta_j * r_{i,j} * f_{i,j}
\label{eq:proba_click}
\end{align}

\section{Probability of the query match user intention}
Because we remove equation that depends on $\alpha_2$, we can now set $\alpha_1$ as MLE.
\begin{align*}
P(M_i = 1) 
&= \alpha_1 \\
\end{align*}

\section{Probability of user submit next query}
User submit next query if the query does not match user intention ($\alpha_1$) or user want to search more.
\begin{align*}
P(N_i=1) 
&= \frac{1}{|S|} \sum_{i\in S} \mathcal{I}(N_i=1) \\
&= \frac{q_i}{|S|} \\
&= n_i
\end{align*}

$q_i$ is the number of submitted-queries where user submit another query after $i$-th query session.

\begin{align*}
P(N_i=1|M_i=1) 
&= \alpha_2 \\
&= \frac{P(N_i=1) - P(N_i=1|M_i=0)P(M_i=0)}{P(M_i=1)} \\
&= \frac{n_i + \alpha_1 - 1}{\alpha_1}
\end{align*}

\section{Relevance probability}
\begin{align*}
P(R_{i,j} = 1)
&= r_{i,j} \\
&= \frac{\sum_{q_{i,j} \in S_{i,j}} P(R_{i,j}=1 | C)}{|S_{i,j}|}
\end{align*}

Where $S_{i,j}$ are all sessions (queries) containing the document corresponding with the query $i$ at rank $j$ - document
$P(R_{i,j}=1 | C)$ will be derive on eq.\ref{eq:proba_relevant_given_click}

\begin{align}
P(R_{i,j}=1 | C)
&= \mathcal{I}(C_{i,j} = 1) P(R_{i,j}|C_{i,j}=1) + \mathcal{I}(C_{i,j} = 0) P(R_{i,j}|C_{i,j}=0) \\
&= c_{i,j} + (1-c_{i,j}) \frac {P(C_{i,j}=0|R_{i,j}=1) P(R_{i,j} = 1)} {P(C_{i,j} = 0)} \\
&= c_{i,j} + (1-c_{i,j}) \frac {P(C_{i,j}=0|R_{i,j}=1) r_{i,j}} { 1 - P(C_{i,j} = 1)}
\label{eq:proba_relevant_given_click}
\end{align}
Where $c_{i,j} = 1$ if (i,j) was clicked in the current session.
$P(C_{i,j}=0|R_{i,j}=1)$ is the chance of no click given that it is relevant. 

\begin{align*}
P(C_{i,j}=0|R_{i,j}=1) 
&= P(C_{i,j }=0|R_{i,j}=1, M_i = 1) P(M_i=1) + P(C_{i,j }=0|R_{i,j}=1, M_i = 0)P(M_i=0) \\
&= \alpha_1 P(C_{i,j }=0|R_{i,j}=1, M_i = 1, E_{i,j}=1) P(E_{i,j}=1)\\     &+ \alpha_1 P(C_{i,j }=0|R_{i,j}=1, M_i = 1, E_{i,j}=0) P(E_{i,j}=0)\\
&+ (1-\alpha_1) P(C_{i,j }=0|R_{i,j}=1 , M_i = 0, E_{i,j}=1) P(E_{i,j}=1)\\
&+ (1-\alpha_1) P(C_{i,j }=0|R_{i,j}=1 , M_i = 0, E_{i,j}=0) P(E_{i,j}=0) \\
\\
&= \alpha_1 \beta_j P(C_{i,j }=0|R_{i,j}=1, M_i = 1, E_{i,j}=1, F_{i,j}=1) P(F_{i,j}=1)\\
&+ \alpha_1 \beta_j P(C_{i,j }=0|R_{i,j}=1, M_i = 1, E_{i,j}=1, F_{i,j}=0) P(F_{i,j}=0)\\
&+ \alpha_1 (1-\beta_j) P(C_{i,j }=0|R_{i,j}=1 , M_i = 1, E_{i,j}=0, F_{i,j}=1) P(F_{i,j}=1)\\
&+ \alpha_1 (1-\beta_j) P(C_{i,j }=0|R_{i,j}=1 , M_i = 1, E_{i,j}=0, F_{i,j}=0) P(F_{i,j}=0)\\
&+ (1-\alpha_1) \beta_j P(C_{i,j }=0|R_{i,j}=1, M_i = 0, E_{i,j}=1, F_{i,j}=1) P(F_{i,j}=1)\\
&+ (1-\alpha_1) \beta_j P(C_{i,j }=0|R_{i,j}=1, M_i = 0, E_{i,j}=1, F_{i,j}=0) P(F_{i,j}=0)\\
&+ (1-\alpha_1) (1-\beta_j) P(C_{i,j }=0|R_{i,j}=1 , M_i = 0, E_{i,j}=0, F_{i,j}=1) P(F_{i,j}=1)\\
&+ (1-\alpha_1) (1-\beta_j) P(C_{i,j }=0|R_{i,j}=1 , M_i = 0, E_{i,j}=0, F_{i,j}=0) P(F_{i,j}=0)\\
\end{align*}
We note that $P(C_{i,j }=0|R_{i,j}=1, M_i = 1, E_{i,j}=1, F_{i,j}=1) = 0$. Otherwise it is $1$. From eq. 24 from TCM paper. Together with inserting our parameters this gives us the following:

\begin{align}
P(C_{i,j}=0|R_{i,j}=1) &= 
\alpha_1 \beta_j f_{i,j} +
\alpha_1 \beta_j (1-f_{i,j}) + 
\alpha_1 (1-\beta_j) f_{i,j} +
\alpha_1 (1-\beta_j) (1-f_{i,j}) \\
&+ (1-\alpha_1) \beta_j f_{i,j} +
(1-\alpha_1) \beta_j (1-f_{i,j}) +
(1-\alpha_1) (1-\beta_j) (f_{i,j} \\
&+(1-\alpha_1) (1-\beta_j) (1-f_{i,j})
\end{align}

expanding this we are only left with
\begin{align}
P(C_{i,j}=0|R_{i,j}=1) = 1 - (\alpha_1 \beta_j f_{i,j})
\label{eq:chance_no_click_given_relevant}
\end{align}
Which seems intuitive as we assumed that all $M_i, R_{i,j}, E_{i,j}$ and $F_{i,j}$ are independent to get $P(C_{i,j} = 1)$ . With this information we can calculate 
\begin{align}
P(R_{i,j}=1 | C) &= c_{i,j} + (1-c_{i,j}) \frac { (1 - (\alpha_1 \beta_j f_{i,j}))  r_{i,j}} { 1 - \alpha_1 \beta_j f_{i,j} r_{i,j} } \\
&= c_{i,j} + (1-c_{i,j}) \frac{r_{i,j} - \alpha_1 \beta_j f_{i,j} r_{i,j} }{ 1 - \alpha_1 \beta_j f_{i,j} r_{i,j}}
\end{align}

\section{Examination probability}
\begin{align}
P(E_{i,j} = 1) 
&= \beta_j \\
&= \frac{1}{|S|} \sum_{i \in S} P(E_{i,j}=1 | C)
\end{align}
Where $S$ is all sessions and $i$ is a query within that session.
$P(E_{i,j}=1 | C)$ will be derive on eq.\ref{eq:proba_examined_given_click}

\begin{align}
\label{eq:proba_examined_given_click}
P(E_{i,j}=1 | C)
&= \mathcal{I}(C_{i,j} = 1) P(E_{i,j}|C_{i,j}=1) + \mathcal{I}(C_{i,j} = 0) P(E_{i,j}|C_{i,j}=0) \\
&= c_{i,j} + (1-c_{i,j}) \frac {P(C_{i,j}=0|E_{i,j}=1) P(E_{i,j} = 1)} {P(C_{i,j} = 0)} \\
&= c_{i,j} + (1-c_{i,j}) \frac {P(C_{i,j}=0|E_{i,j}=1) \beta_j} { 1 - P(C_{i,j} = 1)}
\end{align}
Where $c_{i,j}$ indicates whether document $i,j$ was clicked.
Analog to eq \ref{eq:chance_no_click_given_relevant} we can show that
\begin{align}
P(C_{i,j}=0|E_{i,j}=1) = 1 - (\alpha_1 f_{i,j} r_{i,j})
\end{align}

This gives us 
\begin{align}
P(E_{i,j}=1 | C) 
&= c_{i,j} + (1-c_{i,j}) \frac {( 1 - (\alpha_1 f_{i,j} r_{i,j}) )\beta_j} { 1 - \alpha_1 \beta_j f_{i,j} r_{i,j}} \\
& = c_{i,j} + (1-c_{i,j}) \frac {\beta_j - \alpha_1 \beta_j f_{i,j} r_{i,j}} { 1 - \alpha_1 \beta_j f_{i,j} r_{i,j}}
\end{align}

\section{Freshness probability}
\begin{align}
P(F_{i,j} = 1 | H_{i,j} = 1) &= \alpha_3 \\
\alpha_3 &= \frac{1}{|S_{i,j}|} \sum_{q \in S} \sum_{(i,j) \in q} P(F{i,j}=1 | H_{i,j}=1, C)
\label{eq:freshness}
\end{align}

Where (i,j) is a query, rank pair identifying a certain document.
$P(F_{i,j}=1 | C)$ will be derive on eq.\ref{eq:proba_freshness_given_click} \\
$P(F_{i,j}=1)$ will be derive on eq.\ref{eq:proba_freshness}

\begin{align}
\label{eq:proba_freshness_given_click}
P(F_{i,j}=1 | H_{i,j}=1, C)
&= \mathcal{I}(C_{i,j} = 1) P(F_{i,j}=1|H_{i,j}=1,C_{i,j}=1) \\
&+ \mathcal{I}(C_{i,j} = 0) P(F_{i,j}=1|H_{i,j}=1,C_{i,j}=0) \\
&= c_{i,j} + (1-c_{i,j}) \frac {P(C_{i,j}=0|F_{i,j}=1,H_{i,j}=1) P(F_{i,j} = 1 | H_{i,j}=1)} {P(C_{i,j} = 0 | H_{i,j} = 1)}
\end{align}

Analog to eq \ref{eq:chance_no_click_given_relevant} we can show that
\begin{align}
P(C_{i,j}=0|F_{i,j}=1, H_{i,j}=1) &= 1 - (\alpha_1 \beta_j r_{i,j})
\label{eq:no_click_freshness}
\end{align}
We can also show
\begin{align}
P(C_{i,j}=0|H_{i,j}=1) 
&= 1 - P(C_{i,j}=1|H_{i,j}=1) \\
&= 1-(\alpha_1 \alpha_3 \beta_j r_{i,j})
\end{align}
The only difference between this and eq.  \ref{eq:proba_click} is that it is given that $H_{i,j}=1$ and because $H_{i,j} = 1$ only has an influence on $P(F_{i,j}=1)$, namely that $P(F_{i,j}=1 | H_{i,j} = 1) = 1$, we can substitute $f_{i,j}$ with $\alpha3$ in eq. \ref{eq:proba_click}\\
\\
Now we only need to calculate $f_{i,j} = P(F_{i,j}) = 1$
\begin{align}
\label{eq:proba_freshness}
P(F_{i,j} = 1)
&= \mathcal{I}(H_{i,j}=1) P(F_{i,j}=1|H_{i,j}=1) + \mathcal{I}(H_{i,j}=0) P(F_{i,j}=1|H_{i,j}=0) \\
&= \mathcal{I}(H_{i,j}=1) \alpha_3 + \mathcal{I}(H_{i,j}=0)
\end{align}
Where $\mathcal{I}(H_{i,j}=1)$ is a binary indicator function from the data specifying whether document $(i,j)$ was shown before in the current ($q$ from eq. \ref{eq:freshness}) session.\\

We could replace this indicator function with the probability that the document was examined the last time it was shown. This probability, called $H_{i,j}$ would depend on the probability that it was examined and $H_{i',j'}$ where $i',j'$ is the last time this document was shown in the current session. It would look like this

\begin{align}
P(H_{i,j} = 1) 
&= P(E_{i',j'} = 1) P(H_{i',j'} = 1)
\end{align}

then eq. \ref{eq:proba_freshness} becomes: 
\begin{align}
P(F_{i,j} = 1) 
&= P(H_{i,j}=1) \alpha_3 + P(H_{i,j}=0) \\
&= P(H_{i,j}=1) \alpha_3 + (1 - P(H_{i,j}=1)) \\
&= \alpha_3 P(E_{i',j'} = 1) P(H_{i',j'} = 1) + (1 -  P(E_{i',j'} = 1) P(H_{i',j'} = 1))
\end{align}
Note that this discards the information that if $(i',j')$ was clicked it surely was examined. 

With eq \ref{eq:no_click_freshness} we can calculate $P(F_{i,j}=1 | C)$
\begin{align}
P(F_{i,j}=1 | H=1, C) 
&= c_{i,j} + (1-c_{i,j}) \frac {(1 - (\alpha_1 \beta_j r_{i,j})) \alpha_3} { 1 - \alpha_1 \alpha_3 \beta_j r_{i,j}} \\
&= c_{i,j} + (1-c_{i,j}) \frac {\alpha_3 - \alpha_1 \alpha_3 \beta_j r_{i,j}}{ 1 - \alpha_1 \alpha_3 \beta_j r_{i,j}}
\end{align}